\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-21 doc/sw-system.tex
Add reference to Waterhouse to sec 5.1
Notes on offline performance, closes #148

The dot-dashed curves show the impact of the offline analysis. At \StageOne the
results are very similar to the online version that was actually run (solid
line). However, at \StageTwo there is marginal evidence of there being greater
benefit to doing the analysis offline (\Sref{sec:swap:offline}).
Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
willing to accept a false positive rate of 5\%, the true positive rate rises to
over 95\%, showing that some of the sims that were missed in the online analysis
may be being recovered by doing the analysis offline. The same is true at
\StageOne, but to a lesser extent. Assuming Poisson statistics for the
fluctuations in the numbers of recovered lenses, the uncertainty in the measured
\StageTwo TPR values is around 8\%, but the online and offline samples are
highly correlated, such that the uncertainty on the difference between the ROC
curves is somewhat less than this. Still, a larger validation set is needed to
test these algorithmic choices more rigorously. At \StageOne, high TPR can be
measured to better than 1\%.

@@

Finally, there could be some performance gains to be made by improving the
SWAP agent model, or its implementation. Low skill is typically a result  of
inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
inexperienced as well as the classifier or its agent. In a future paper we
plan to investigate the use of the test images as well as the training images
in accelerating the agent's learning (Davis et al, in preparation). We also
plan to investigate the use of offline analysis at \StageOne, for the same
reason (see also \Sref{sec:discuss:efficiency} below.)
One might also consider looking at
introducing more conditional dependences in the confusion matrix elements, to
allow for some classifiers having greater skill in spotting one type of lens
than another, or, more generally, as a function of lens property (such as
colour, brightness, and image separation). In the current model, all agents are
considered to be completely independent, whereas in fact we might expect there
to be significant clustering of the confusion matrix elements in the $\PD - \PL$
plane. A hierarchical
model for the crowd, with hyper-parameters describing the distribution of
confusion matrix elements across the population, may well accelerate the agent
learning process by including the notion of one agent being likely to be
similar to its neighbours. Finally, it is worth noting that the model of
\citet{IBCC} explicitly avoids the assumption of the agent confusion matrix
elements being constant in time (as was assumed in \Sref{sec:swap}),
allowing the development of volunteer skill
to be more accurately tracked -- and that they did see some time-evolution in
the supernova zoo classifiers' skill. Finding a way to incorporate such a
learning model into SWAP while retaining its online character
is an interesting challenge for future work.

>>>>

The dot-dashed curves show the results from the offline analysis. At \StageOne the
results are very similar to the online version that was actually run (solid
line). However, at \StageTwo there is marginal evidence of there being greater
benefit to doing the analysis offline (\Sref{sec:swap:offline}).
Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
willing to accept a false positive rate of 5\%, the true positive rate rises to
over 95\%, showing that some of the sims that were missed in the online analysis
may be being recovered by doing the analysis offline. (The same is true at
\StageOne, but to a lesser extent.) One interpretation for this result (if it holds up)
would be that the offline analysis, by using each agent's entire history, is
making less noisy probability estimates.

Assuming Poisson statistics for the
fluctuations in the numbers of recovered lenses, the uncertainty in the measured
\StageTwo TPR values is around 8\%, but the online and offline samples are
highly correlated, such that the uncertainty on the {\it difference} between the ROC
curves is somewhat less than this. Still, a larger validation set is needed to
test these algorithmic choices more rigorously. At \StageOne, high TPR can be
measured to better than 1\%.

@@

Finally, there could be some performance gains to be made by improving the SWAP
agent model, or its implementation. Low skill is typically a result  of
inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
inexperienced as well as the classifier or its agent. In a future paper we plan
to investigate the use of the test images as well as the training images in
accelerating the agent's learning (Davis et al, in preparation). We also plan to
investigate the use of offline analysis at \StageOne, partly for the same reason
(see also \Sref{sec:discuss:efficiency} below.) Given the above findings  about
the effects of noise in the SWAP system, we are also motivated to explore
further the possible noise-reducing effects of the doing the analysis offline
(\Sref{sec:results:sample}).

One might also consider looking at
introducing more conditional dependences in the confusion matrix elements, to
allow for some classifiers having greater skill in spotting one type of lens
than another, or, more generally, as a function of lens property (such as
colour, brightness, and image separation). In the current model, all agents are
considered to be completely independent, whereas in fact we might expect there
to be significant clustering of the confusion matrix elements in the $\PD - \PL$
plane. A hierarchical
model for the crowd, with hyper-parameters describing the distribution of
confusion matrix elements across the population, may well accelerate the agent
learning process by including the notion of one agent being likely to be
similar to its neighbours. Finally, it is worth noting that the model of
\citet{IBCC} explicitly avoids the assumption of the agent confusion matrix
elements being constant in time (as was assumed in \Sref{sec:swap}),
allowing the development of volunteer skill
to be more accurately tracked -- and that they did see some time-evolution in
the supernova zoo classifiers' skill. Finding a way to incorporate such a
learning model into SWAP while retaining its online character
is an interesting challenge for future work.
